supplementary figures

### 2019-10-03 SuppFigures.Rmd
change figure sizes/labeling

---
title: "supplementary figures"
author: "Taryn McLaughlin"
date: "9/26/2019"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, comment=NA, warning=FALSE, echo=FALSE)
library(dplyr)
library(knitr)
library(ggplot2)
library(gridExtra)
library(GGally)
library(ggpubr)
library(cowplot)
library(tidyr)
library(reshape2)
library(cowplot)
library(corrplot)
library(sjPlot)
```

```{r plot functions}
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/tryna function.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/pvals_TB-SM.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/plot_functions.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/comp_hc_ltbi.R")

baseplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=SM))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ theme(legend.position="none")+
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    theme(text = element_text(size=20),
          axis.text.x = element_text(size = 16),
          strip.text = element_text(size = 20))+
    theme(plot.title = element_text(hjust = 0.5, size=20)) +
    labs(x="", y="")
}

booleanplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=SM))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    theme(legend.position="none")+
    theme(text = element_text(size=20), 
          axis.text.x = element_text(size=16), 
          strip.text = element_text(size = 20))+
    theme(plot.title = element_text(hjust = 0.5, size=20)) +
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10)+
    labs(x="", y="")
}

allplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=disease))+
    geom_boxplot(size=1, position=position_dodge2(width=0.2, padding = 0.2, preserve = "single"), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    theme(legend.position="none") +
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    facet_wrap(~variable)+
    theme(text = element_text(size=20),
            axis.text.x = element_text(size = 16),
            strip.text = element_text(size = 20))+
    theme(plot.title = element_text(hjust = 0.5, size=20))+
    labs(x="", y="")
}

cyt_groups <- as_labeller(c("IFNg" = "IFNγ", 
                    "TNFa" = "TNFα", "IL4" = "IL-4", "IL13" = "IL-13"))

all_comps<-list(c("HC SM+", "HC SM-"),c("LTBI SM+", "LTBI SM-"), c("TB SM+", "TB SM-"))

healthy.cols<- c("SM+" = "#1a9850", "SM-" ="#91cf60")
ltbi.cols<- c("SM+" = "#2166ac", "SM-" = "#85ABD1")
tb.cols<- c("SM+" = "#b2182b", "SM-"="#E59EA6")
all.cols<- c("Naive" = "#C8D0D8","HC SM+" = "#1a9850", "HC SM-" ="#91cf60",
             "LTBI SM+" = "#2166ac", "LTBI SM-" = "#85ABD1",
             "TB SM+" = "#b2182b", "TB SM-"="#E59EA6")
```

```{r load data}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean/")
CD4<-read.csv("ICS_CD4_clean.csv")
CYT<-read.csv("ICS_CD4_Cytokine_clean.csv")
PHEN<-read.csv("ICS_CD4_phenotyping_clean_NAs.csv")
OG<-data.table(read.csv("OG_CD4_bulk_summary_clean.csv"))
OGPHEN<-read.csv("OG_CD4_OG_summary_clean_NAs.csv")
OGnope<-read.csv("OG_CD4_noOG_summary_clean.csv")
OG.IFNg<-read.csv("OG_CD4_OG.IFNg_summary_clean_NAs.csv")
OG.GT<-read.csv("OG_CD4_OG.GT_summary_clean_NAs.csv")
OG.th1<-read.csv("OG_CD4_OG.TH1_summary_clean_NAs.csv")
luminex<-read.csv("/Applications/Old Computer/Day Lab/Luminex/Clean Data/Luminex_combined_background.txt")
```

##ICS Supplementary
```{r}
booleanplot2<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=disease))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    theme(legend.position="none")+
    theme(text = element_text(size=20), axis.text.x = element_text(size=20))+
    theme(plot.subtitle = element_text(hjust = 0.5)) +
    labs(x="", y="")
}
```

###Boolean PMA
*but I need to make them pretty and I dont' feel like doing that right now*
```{r boolean pma cyt, fig.width=15, fig.height=12}
cyt<-plot_filter(CYT[CYT$Stim=="PMA",])
test<-melt(cyt, id.vars=c("TB", "SM", "disease"), measure.vars = grep("._._._.|._._.._.", names(cyt)))
test<-test[-grep("tbet|gata3|x_x_x_x", test$variable),]
test$variable<-factor(test$variable, levels=c(
"G_4_13_T", "G_4_x_T", "G_x_13_T", "G_4_13_x", "x_4_13_T","G_4_x_x", "G_x_13_x","x_4_x_T","x_x_13_T",
"G_x_x_T" , "G_x_x_x","x_x_x_T",
"x_4_13_x","x_4_x_x", "x_x_13_x"
))

G   <-c("+", "+", "+", "+", "-", "+", "+", "-", "-", "+", "+", "-", "-", "-", "-")
il4 <-c("+", "+", "-", "+", "+", "+", "-", "+", "-", "-", "-", "-", "+", "+", "-")
il13<-c("+", "-", "+", "+", "+", "-", "+", "-", "+", "-", "-", "-", "+", "-", "+")
T   <-c("+", "+", "+", "-", "+", "-", "-", "+", "+", "+", "-", "+", "-", "-", "-")

labels <- paste0(G, "\n", T, "\n", il4, "\n", il13)
breaks <- levels(test$variable)

@@

th1.2<-booleanplot2(test[test$th=="TH1/2",], "variable", "value", all.cols)+facet_grid(TB~th, scales="free", space="free")+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10, label.y = 20)+
    coord_cartesian(ylim=c(0,3))+
    theme(strip.text.y = element_blank(), strip.background.y = element_blank())+
    labs(y="(%) CD4 T cells")

th1<-booleanplot2(test[test$th=="TH1",], "variable", "value", all.cols)+facet_grid(TB~th, scales="free", space="free")+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10, label.y = 20)+
    coord_cartesian(ylim=c(0,25))+
    theme(strip.text.y = element_blank(), strip.background.y = element_blank())

th2<-booleanplot2(test[test$th=="TH2",], "variable", "value", all.cols)+facet_grid(TB~th, scales="free", space="free")+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10, label.y = 20)+
    coord_cartesian(ylim=c(0,3))

supp1<-cowplot::plot_grid(th1.2, th1, th2, ncol=3, rel_widths = c(8,3.5,3.5))
```

###Boolean Phenotypes
###TH1
```{r pma th1 boolean, fig.width=20, fig.height=18}
phen<-plot_filter(subset(PHEN, PHEN$Stim=="PMA"))

melt<-melt(phen, id.vars=c("TB", "SM", "disease"), measure.vars = grep("TH1_._._._.", names(phen)))
test<-filter(melt, variable!="TH1_x_x_x_x")
test$variable<-gsub("TH1_", "", test$variable)
test$variable<-factor(test$variable, levels=c(
"t_x_3_4" ,       
"t_x_3_x" ,         
"t_x_x_4" ,         
"t_x_x_x" ,
"t_g_3_4" ,         
"t_g_3_x" ,         
"t_g_x_4" ,         
"t_g_x_x" ,
"x_g_3_4" ,         
"x_g_3_x" ,         
"x_g_x_4" ,         
"x_g_x_x" ,
"x_x_3_4" ,          
"x_x_3_x" ,         
"x_x_x_4"           
))

T <- c("+", "+","+","+","+","+","+","+","-","-","-","-","-","-","-")
G <- c("-","-","-","-","+", "+","+","+","+","+","+","+","-","-","-")
c3 <-c("+", "+","-","-","+", "+","-","-","+", "+","-","-","+", "+","-")
c4 <-c("+","-","+","-","+","-","+","-","+","-","+","-","+","-","+")

labels <- paste0(T, "\n", G, "\n", c3, "\n", c4)
breaks <- levels(test$variable)

df<-data.frame(cbind(levels(test$variable),T,G,c3,c4))
dfm<-melt(df, measure.vars=c("T", "G","c3","c4"))
dfm$variable<-factor(dfm$variable, levels=c("c4","c3","G", "T"))

data_table <- ggplot(dfm, aes(x = V1, y = variable, label = format(value))) +
    geom_text(size = 10) + 
    theme_bw() + 
    labs(x="",y="")+
    theme(strip.text.x = element_blank(), strip.background.x = element_blank())+
    scale_y_discrete(labels=c("T-bet", "GATA3", "CXCR3", "CCR4"))+
    theme(axis.text.y = element_text(size=20))+
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          axis.title = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks = element_blank())

@@

supp2a<-booleanplot2(test, "variable", "value", all.cols)+
    facet_grid(TB~tf, scales="free_x")+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10, label.y = 40)+
    coord_cartesian(ylim=c(0,65))

```
###TH2  
```{r pma th2 boolean, fig.width=20, fig.height=18}
phen<-plot_filter(subset(PHEN, PHEN$Stim=="PMA"))

melt<-melt(phen, id.vars=c("TB", "SM", "disease"), measure.vars = grep("TH2_._._._.", names(phen)))
test<-filter(melt, variable!="TH2_x_x_x_x")
test$variable<-gsub("TH2_", "", test$variable)
test$variable<-factor(test$variable, levels=c(
"t_x_3_4" ,       
"t_x_3_x" ,         
"t_x_x_4" ,         
"t_x_x_x" ,
"t_g_3_4" ,         
"t_g_3_x" ,         
"t_g_x_4" ,         
"t_g_x_x" ,
"x_g_3_4" ,         
"x_g_3_x" ,         
"x_g_x_4" ,         
"x_g_x_x" ,
"x_x_3_4" ,          
"x_x_3_x" ,         
"x_x_x_4"           
))

T <- c("+", "+","+","+","+","+","+","+","-","-","-","-","-","-","-")
G <- c("-","-","-","-","+", "+","+","+","+","+","+","+","-","-","-")
c3 <-c("+", "+","-","-","+", "+","-","-","+", "+","-","-","+", "+","-")
c4 <-c("+","-","+","-","+","-","+","-","+","-","+","-","+","-","+")

labels <- paste0(T, "\n", G, "\n", c3, "\n", c4)
breaks <- levels(test$variable)

@@

supp2b<-booleanplot2(test, "variable", "value", all.cols)+
    facet_grid(TB~tf, scales="free_x")+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10, label.y = 40)+
    coord_cartesian(ylim=c(0,65))
```

```{r}
supp2<-cowplot::plot_grid(supp2a, supp2b, nrow=2, labels=c("A", "B"))
```

###Peptide-Specific Cytokine Production  
```{r, fig.width=15, fig.height=8}
melt<-melt(subset(CYT, CYT$Stim=="PEP"), 
           id.vars=c("TB","SM"), 
           measure.vars=c("TH1.Freq", "TH1.2.Freq", "TH2.Freq"))
th_groups <- as_labeller(c("TH1.Freq" = "TH1", 
                    "TH1.2.Freq" = "TH1/2", "TH2.Freq" = "TH2"))

cyt<-filter_ltbi(melt)
b<-baseplot(cyt, "SM", "value", ltbi.cols)+
    facet_wrap(~variable, ncol=4, labeller=th_groups)+
    coord_cartesian(ylim=c(0,.2))

cyt<-filter_tb(melt)
c<-baseplot(cyt, "SM", "value", tb.cols)+
    facet_wrap(~variable, ncol=4, labeller=th_groups)+
    coord_cartesian(ylim=c(0,.2))

supp3<-cowplot::plot_grid(b, c, ncol=3)
```

```{r, fig.width=16, fig.height=8}
cyt<-plot_filter(CYT[CYT$Stim=="PEP",])
test<-melt(cyt, id.vars=c("TB", "SM", "disease"), measure.vars = grep("._._._.|._._.._.", names(cyt)))
test<-test[-grep("tbet|gata3|x_x_x_x", test$variable),]
test$variable<-factor(test$variable, levels=c(
"G_4_13_T", "G_4_x_T", "G_x_13_T", "G_4_13_x", "x_4_13_T","G_4_x_x", "G_x_13_x","x_4_x_T","x_x_13_T",
"G_x_x_T" , "G_x_x_x","x_x_x_T",
"x_4_13_x","x_4_x_x", "x_x_13_x"
))

G   <-c("IFNγ +", "+", "+", "+", "-", "+", "+", "-", "-", "+", "+", "-", "-", "-", "-")
il4 <-c("IL-4 +", "+", "-", "+", "+", "+", "-", "+", "-", "-", "-", "-", "+", "+", "-")
il13<-c("IL-13 +", "-", "+", "+", "+", "-", "+", "-", "+", "-", "-", "-", "+", "-", "+")
T   <-c("TNFα +", "+", "+", "-", "+", "-", "-", "+", "+", "+", "-", "+", "-", "-", "-")

labels <- paste0(G, "\n", T, "\n", il4, "\n", il13)
breaks <- levels(test$variable)

@@

supp4a<-booleanplot2(test[test$TB=="LTBI",], "variable", "value", all.cols)+facet_grid(TB~th, scales="free", space="free")+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, exact=FALSE, size=10)+
    coord_cartesian(ylim=c(0,.16))+
    labs(y="(%) CD4 T cells")

supp5a<-booleanplot2(test[test$TB=="TB",], "variable", "value", all.cols)+facet_grid(TB~th, scales="free", space="free")+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, exact=FALSE, size=10)+
    coord_cartesian(ylim=c(0,.15))+
    labs(y="(%) CD4 T cells")
```

###Peptide Mtb-specific TH1 Cytokine+ Cell Phenotypes
```{r ics phenotyping, fig.width=16, fig.height=24}
phen<-filter_ltbi(subset(PHEN, PHEN$Stim=="PEP"))

melt<-melt(phen, id.vars=c("TB", "SM"), measure.vars = grep("TH1_._._._.", names(phen)))
test<-filter(melt, variable!="TH1_x_x_x_x")
test$variable<-gsub("TH1_", "", test$variable)
test$variable<-factor(test$variable, levels=c(
"t_x_3_4" ,       
"t_x_3_x" ,         
"t_x_x_4" ,         
"t_x_x_x" ,
"t_g_3_4" ,         
"t_g_3_x" ,         
"t_g_x_4" ,         
"t_g_x_x" ,
"x_g_3_4" ,         
"x_g_3_x" ,         
"x_g_x_4" ,         
"x_g_x_x" ,
"x_x_3_4" ,          
"x_x_3_x" ,         
"x_x_x_4"           
))

T <- c("+", "+","+","+","+","+","+","+","-","-","-","-","-","-","-")
G <- c("-","-","-","-","+", "+","+","+","+","+","+","+","-","-","-")
c3 <-c("+", "+","-","-","+", "+","-","-","+", "+","-","-","+", "+","-")
c4 <-c("+","-","+","-","+","-","+","-","+","-","+","-","+","-","+")

labels <- paste0(T, "\n", G, "\n", c3, "\n", c4)
breaks <- levels(test$variable)

>>>>

---
title: "supplementary figures"
author: "Taryn McLaughlin"
date: "9/26/2019"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, comment=NA, warning=FALSE, echo=FALSE)
library(dplyr)
library(knitr)
library(ggplot2)
library(gridExtra)
library(GGally)
library(ggpubr)
library(cowplot)
library(tidyr)
library(reshape2)
library(cowplot)
library(corrplot)
library(sjPlot)
library(ggsignif)
```

```{r plot functions}
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/tryna function.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/pvals_TB-SM.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/plot_functions.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/comp_hc_ltbi.R")
```

```{r load data}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean/")
CD4<-read.csv("ICS_CD4_clean.csv")
CYT<-read.csv("ICS_CD4_Cytokine_clean.csv")
PHEN<-read.csv("ICS_CD4_phenotyping_clean_NAs.csv")
OG<-read.csv("OG_CD4_bulk_summary_clean.csv")
OGPHEN<-read.csv("OG_CD4_OG_summary_clean_NAs.csv")
OGnope<-read.csv("OG_CD4_noOG_summary_clean.csv")
OG.IFNg<-read.csv("OG_CD4_OG.IFNg_summary_clean_NAs.csv")
OG.GT<-read.csv("OG_CD4_OG.GT_summary_clean_NAs.csv")
OG.th1<-read.csv("OG_CD4_OG.TH1_summary_clean_NAs.csv")
luminex<-read.csv("/Applications/Old Computer/Day Lab/Luminex/Clean Data/Luminex_combined_background.txt")
```

```{r, all the labels I use multiple times}
#cytokines
G   <-c("+", "+", "+", "+", "-", "+", "+", "-", "-", "+", "+", "-", "-", "-", "-")
il4 <-c("+", "+", "-", "+", "+", "+", "-", "+", "-", "-", "-", "-", "+", "+", "-")
il13<-c("+", "-", "+", "+", "+", "-", "+", "-", "+", "-", "-", "-", "+", "-", "+")
T   <-c("+", "+", "+", "-", "+", "-", "-", "+", "+", "+", "-", "+", "-", "-", "-")

cyt_labels <- paste0(G, "\n", T, "\n", il4, "\n", il13)
cyt_breaks <- c(
"G_4_13_T", "G_4_x_T", "G_x_13_T", "G_4_13_x", "x_4_13_T","G_4_x_x", "G_x_13_x","x_4_x_T","x_x_13_T",
"G_x_x_T" , "G_x_x_x","x_x_x_T",
"x_4_13_x","x_4_x_x", "x_x_13_x")

#TH groups
th_groups <- as_labeller(c("TH1.Freq" = "TH1", 
                    "TH1.2.Freq" = "TH1/2", "TH2.Freq" = "TH2"))

#Phenotype boolean labels
T <- c("+", "+","+","+","+","+","+","+","-","-","-","-","-","-","-")
G <- c("-","-","-","-","+", "+","+","+","+","+","+","+","-","-","-")
c3 <-c("+", "+","-","-","+", "+","-","-","+", "+","-","-","+", "+","-")
c4 <-c("+","-","+","-","+","-","+","-","+","-","+","-","+","-","+")

phen_labels <- paste0(T, "\n", G, "\n", c3, "\n", c4)
phen_breaks <- c(
"t_x_3_4" , "t_x_3_x" , "t_x_x_4" , "t_x_x_x" ,
"t_g_3_4" , "t_g_3_x" , "t_g_x_4" , "t_g_x_x" ,
"x_g_3_4" , "x_g_3_x" , "x_g_x_4" , "x_g_x_x" ,
"x_x_3_4" , "x_x_3_x" , "x_x_x_4")
```

#ICS Supplementary

##2 Boolean PMA
```{r}
cyt<-plot_filter(CYT[CYT$Stim=="PMA",])
test<-melt(cyt, id.vars=c("TB", "SM", "disease"), measure.vars = grep("._._._.|._._.._.", names(cyt)))
test<-test[-grep("tbet|gata3|x_x_x_x", test$variable),]
test$variable<-factor(test$variable, levels=c(
"G_4_13_T", "G_4_x_T", "G_x_13_T", "G_4_13_x", "x_4_13_T","G_4_x_x", "G_x_13_x","x_4_x_T","x_x_13_T",
"G_x_x_T" , "G_x_x_x","x_x_x_T",
"x_4_13_x","x_4_x_x", "x_x_13_x"
))

@@

th1.2<-booleanplot2(test[test$th=="TH1/2",], "variable", "value", all.cols)+facet_grid(TB~th, scales="free", space="free")+
    scale_x_discrete(labels = cyt_labels, breaks=cyt_breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10, label.y = 20)+
    coord_cartesian(ylim=c(0,3))+
    theme(strip.text.y = element_blank(), strip.background.y = element_blank())+
    labs(y="(%) CD4 T cells")

th1<-booleanplot2(test[test$th=="TH1",], "variable", "value", all.cols)+facet_grid(TB~th, scales="free", space="free")+
    scale_x_discrete(labels = cyt_labels, breaks=cyt_breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10, label.y = 20)+
    coord_cartesian(ylim=c(0,25))+
    theme(strip.text.y = element_blank(), strip.background.y = element_blank())

th2<-booleanplot2(test[test$th=="TH2",], "variable", "value", all.cols)+facet_grid(TB~th, scales="free", space="free")+
    scale_x_discrete(labels = cyt_labels, breaks=cyt_breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10, label.y = 20)+
    coord_cartesian(ylim=c(0,3))
```

```{r, fig.height=10, fig.width=10}
supp2<-cowplot::plot_grid(th1.2, th1, th2, ncol=3, rel_widths = c(8,3.5,3.5))
supp2
```

##3 PMA Phenotypes
```{r}
phen<-plot_filter(subset(PHEN, PHEN$Stim=="PMA"))

test<-melt(phen, id.vars=c("TB", "SM", "disease"), measure.vars = grep("TH._._._._.", names(phen)))
test$thgroup<-"TH1"
test$thgroup[grep("TH2", test$variable)]<-"TH2"

test<-test[-(grep("x_x_x_x", test$variable)),]
test$variable<-gsub("TH1_", "", test$variable)
test$variable<-gsub("TH2_", "", test$variable)
test$variable<-factor(test$variable, levels=c(
"t_x_3_4" , "t_x_3_x" , "t_x_x_4" , "t_x_x_x" ,
"t_g_3_4" , "t_g_3_x" , "t_g_x_4" , "t_g_x_x" ,
"x_g_3_4" , "x_g_3_x" , "x_g_x_4" , "x_g_x_x" ,
"x_x_3_4" , "x_x_3_x" , "x_x_x_4"))

@@

supp3a<-booleanplot2(test[test$thgroup=="TH1",], "variable", "value", all.cols)+
    facet_grid(TB~tf, scales="free_x")+
    scale_x_discrete(labels = phen_labels, breaks=phen_breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10, label.y = 40)+
    coord_cartesian(ylim=c(0,65))+
    theme(plot.margin=margin(l=1,unit="cm"))+
    labs(y="(%) TH1 Cytokine+ CD4 T cells")

supp3b<-booleanplot2(test[test$thgroup=="TH2",], "variable", "value", all.cols)+
    facet_grid(TB~tf, scales="free_x")+
    scale_x_discrete(labels = phen_labels, breaks=phen_breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10, label.y = 40)+
    coord_cartesian(ylim=c(0,65))+
    theme(plot.margin=margin(l=1,unit="cm"))+
    labs(y="(%) TH2 Cytokine+ CD4 T cells")

```{r, fig.height=12, fig.width=10}
supp3<-cowplot::plot_grid(supp3a, supp3b, nrow=2, labels=c("A", "B"), label_size = 20)
supp3
```

##4 LTBI ICS extra 
```{r}
cyt<-filter_ltbi(CYT[CYT$Stim=="PEP",])

#boolean cytokine
test<-melt(cyt, id.vars=c("TB", "SM", "disease"), measure.vars = grep("._._._.|._._.._.", names(cyt)))
test<-test[-grep("tbet|gata3|x_x_x_x", test$variable),]
test$variable<-factor(test$variable, levels=c(
"G_4_13_T", "G_4_x_T", "G_x_13_T", "G_4_13_x", "x_4_13_T","G_4_x_x", "G_x_13_x","x_4_x_T","x_x_13_T",
"G_x_x_T" , "G_x_x_x","x_x_x_T",
"x_4_13_x","x_4_x_x", "x_x_13_x"
))

a<-booleanplot2(test, "variable", "value", all.cols)+facet_grid(~th, scales="free", space="free")+
    scale_x_discrete(labels = cyt_labels, breaks=cyt_breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, exact=FALSE, size=10)+
    coord_cartesian(ylim=c(0,.16))+
    theme(plot.margin=margin(l=1,unit="cm"))+
    labs(y="(%) CD4 T cells")

#condensed TH cytokine
test<-melt(cyt,
           id.vars=c("TB","SM"), 
           measure.vars=c("TH1.Freq", "TH1.2.Freq", "TH2.Freq"))

b<-baseplot(test, "SM", "value", ltbi.cols)+
    facet_wrap(~variable, ncol=4, labeller=th_groups)+
    coord_cartesian(ylim=c(0,.2))+
    labs(y="(%) CD4 T cells")

#phenotypes
phen<-filter_ltbi(subset(PHEN, PHEN$Stim=="PEP"))

melt<-melt(phen, id.vars=c("TB", "SM"), measure.vars = grep("TH1_._._._.", names(phen)))
test<-filter(melt, variable!="TH1_x_x_x_x")
test$variable<-gsub("TH1_", "", test$variable)
test$variable<-factor(test$variable, levels=c(
"t_x_3_4" , "t_x_3_x" , "t_x_x_4" , "t_x_x_x" ,
"t_g_3_4" , "t_g_3_x" , "t_g_x_4" , "t_g_x_x" ,
"x_g_3_4" , "x_g_3_x" , "x_g_x_4" , "x_g_x_x" ,
"x_x_3_4" , "x_x_3_x" , "x_x_x_4"))

@@

c<-booleanplot(test, "variable", "value", ltbi.cols)+facet_wrap(~tf, scales="free_x",ncol=4)+
    scale_x_discrete(labels = phen_labels, breaks=phen_breaks)+
    theme(legend.position = "right", legend.key.size = unit(4, "cm"))+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10)+
    theme(plot.margin=margin(l=0.5,unit="cm"))+
    labs(y="(%) Mtb-Specific\nTH1 Cytokine+ cells")
```

```{r, fig.height=10, fig.width=12}
#compiling together
suppab<-cowplot::plot_grid(a, b, nrow=1, labels=c("A", "B"), label_size = 20,
                           align="hv", rel_widths = c(6,3))
suppc<-cowplot::plot_grid(c, nrow=1, labels=c("C"), label_size = 20)
supp4<-cowplot::plot_grid(suppab, suppc, align="hv", nrow=2)
supp4
```

##5 Comparing Mtb-specific CD4 T cells to other CD4 T cells in LTBI
```{r}
total<-filter_ltbi(subset(CD4, CD4$Stim=="UN"))
total$cell<-"Total"
phen<-filter_ltbi(subset(PHEN, PHEN$Stim=="PEP"))
names<-c("Donor", "TB", "SM", "Stim", "disease", names(phen)[grep("TH1_", names(phen))])
mtb_th1<-select(phen, names)
names(mtb_th1)<-gsub("TH1_", "", names(mtb_th1))
mtb_th1$cell<-"Mtb-Specific"
long<-rbindlist(list(total, mtb_th1), fill=TRUE)

melt<-melt(long, id.vars=c("TB", "SM", "disease", "cell"), measure.vars=c("T-bet", "GATA3", "CXCR3","CCR4"))
melt$cell<-factor(melt$cell, levels=c("Total", "Mtb-Specific"))
melt$x<-paste(melt$SM, melt$cell, sep=" ")
melt$x<-factor(melt$x, levels=c("SM- Total", "SM- Mtb-Specific","SM+ Total", "SM+ Mtb-Specific"))
melt<-data.frame(melt)

a1<-baseplot(melt[(melt$variable %in% c("T-bet", "GATA3")),], "x", "value", ltbi.cols)+
    facet_wrap(~variable, nrow=1)+
    scale_x_discrete(labels=c("Total", "CFP-10 &\nESAT-6", "Total", "CFP-10 &\nESAT-6"))+
    labs(y="(%) CD4 T cells")+
    geom_signif(
        comparisons=list(c("SM- Mtb-Specific", "SM- Total"),c("SM+ Mtb-Specific", "SM+ Total")),
                test = "wilcox.test", map_signif_level=TRUE, textsize = 6, tip_length = 0.03, y_position = .98*32)+    
    coord_cartesian(ylim=c(0,32))

a2<-baseplot(melt[(melt$variable %in% c("CXCR3", "CCR4")),], "x", "value", ltbi.cols)+
    facet_wrap(~variable, nrow=1)+
    scale_x_discrete(labels=c("Total", "CFP-10 &\nESAT-6", "Total", "CFP-10 &\nESAT-6"))+
    geom_signif(
        comparisons=list(c("SM- Mtb-Specific", "SM- Total"),c("SM+ Mtb-Specific", "SM+ Total")),
                test = "wilcox.test", map_signif_level=TRUE, textsize = 6, tip_length = 0.03, y_position = 98)+    
    coord_cartesian(ylim=c(0,100))
```

```{r}
pma<-filter_ltbi(subset(PHEN, PHEN$Stim=="PMA"))
pma$cell<-"PMA"
pep<-filter_ltbi(subset(PHEN, PHEN$Stim=="PEP"))
pep$cell<-"Mtb"
long<-rbindlist(list(pma, pep), fill=TRUE)
names<-c("Donor", "TB", "SM", "Stim", "disease", "cell", names(long)[grep("TH1_", names(long))])
long<-select(long, names)
names(long)<-gsub("TH1_", "", names(long))

melt<-melt(long, id.vars=c("TB", "SM", "disease", "cell"), measure.vars=c("T-bet", "GATA3", "CXCR3","CCR4"))
melt$x<-paste(melt$SM, melt$cell, sep=" ")
melt$x<-factor(melt$x, levels=c("SM- PMA", "SM- Mtb","SM+ PMA", "SM+ Mtb"))
melt<-data.frame(melt)

b1<-baseplot(melt[(melt$variable %in% c("T-bet", "GATA3")),], "x", "value", ltbi.cols)+
    facet_wrap(~variable, nrow=1)+
    scale_x_discrete(labels=c("PMA", "CFP-10 &\nESAT-6", "PMA", "CFP-10 &\nESAT-6"))+
    labs(y="(%) CD4 T cells")+
    geom_signif(comparisons=list(c("SM- Mtb", "SM- PMA"),c("SM+ Mtb", "SM+ PMA")), 
                test = "wilcox.test", map_signif_level=TRUE, textsize = 6, tip_length = 0.03, y_position = .98*40)+    
    coord_cartesian(ylim=c(0,40))

b2<-baseplot(melt[(melt$variable %in% c("CXCR3", "CCR4")),], "x", "value", ltbi.cols)+
    facet_wrap(~variable, nrow=1)+
    scale_x_discrete(labels=c("PMA", "CFP-10 &\nESAT-6", "PMA", "CFP-10 &\nESAT-6"))+
    geom_signif(comparisons=list(c("SM- Mtb", "SM- PMA"),c("SM+ Mtb", "SM+ PMA")), 
                test = "wilcox.test", map_signif_level=TRUE, textsize = 6, tip_length = 0.03, y_position = 98)+    
    coord_cartesian(ylim=c(0,100))
```

```{r, fig.height=10, fig.width=12}
supp5<-cowplot::plot_grid(a1,a2,b1,b2, ncol=2, labels=c("A","","B",""), label_size = 20)
supp5
```

##6 TB ICS extra
```{r}
cyt<-filter_tb(CYT[CYT$Stim=="PEP",])

#boolean cytokine
test<-melt(cyt, id.vars=c("TB", "SM", "disease"), measure.vars = grep("._._._.|._._.._.", names(cyt)))
test<-test[-grep("tbet|gata3|x_x_x_x", test$variable),]
test$variable<-factor(test$variable, levels=c(
"G_4_13_T", "G_4_x_T", "G_x_13_T", "G_4_13_x", "x_4_13_T","G_4_x_x", "G_x_13_x","x_4_x_T","x_x_13_T",
"G_x_x_T" , "G_x_x_x","x_x_x_T",
"x_4_13_x","x_4_x_x", "x_x_13_x"
))

@@

a<-booleanplot2(test, "variable", "value", all.cols)+facet_grid(~th, scales="free", space="free")+
    scale_x_discrete(labels = cyt_labels, breaks=cyt_breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, exact=FALSE, size=10)+
    coord_cartesian(ylim=c(0,.16))+
    theme(plot.margin=margin(l=1,unit="cm"))+
    labs(y="(%) CD4 T cells")

#condensed TH cytokine
test<-melt(cyt,
           id.vars=c("TB","SM"), 
           measure.vars=c("TH1.Freq", "TH1.2.Freq", "TH2.Freq"))

b<-baseplot(test, "SM", "value", tb.cols)+
    facet_wrap(~variable, ncol=4, labeller=th_groups)+
    coord_cartesian(ylim=c(0,.2))+
    labs(y="(%) CD4 T cells")

#phenotypes
phen<-filter_tb(subset(PHEN, PHEN$Stim=="PEP"))

melt<-melt(phen, id.vars=c("TB", "SM"), measure.vars = grep("TH1_._._._.", names(phen)))
test<-filter(melt, variable!="TH1_x_x_x_x")
test$variable<-gsub("TH1_", "", test$variable)
test$variable<-factor(test$variable, levels=c(
"t_x_3_4" , "t_x_3_x" , "t_x_x_4" , "t_x_x_x" ,
"t_g_3_4" , "t_g_3_x" , "t_g_x_4" , "t_g_x_x" ,
"x_g_3_4" , "x_g_3_x" , "x_g_x_4" , "x_g_x_x" ,
"x_x_3_4" , "x_x_3_x" , "x_x_x_4"))
